Copy number inference with InferCNV

### 2024-06-17 analyses/cell-type-ewings/template_notebooks/03-copykat.Rmd

```{r packages}
suppressPackageStartupMessages({
  # load required packages
  library(SingleCellExperiment)
  library(ggplot2)
  library(copykat)
})

knitr::opts_chunk$set(
  dev = "jpeg"
)
```

@@

# output classifications file 
copykat_results_file <- file.path(params$results_dir, params$sample_id, glue::glue("{params$library_id}_copykat-classifications.tsv"))
```

>>>>

```{r packages}
suppressPackageStartupMessages({
  # load required packages
  library(SingleCellExperiment)
  library(ggplot2)
  library(copykat)
})
```

@@

# output classifications file 
copykat_results_file <- file.path(params$results_dir, glue::glue("{params$library_id}_copykat-classifications.tsv"))
```

### 2024-06-17 analyses/cell-type-ewings/template_notebooks/04-infercnv.Rmd

```{r}
# get a dataframe with barcodes, sum_classification and cluster_classification 
celltypes_df <- cnv_df |> 
  dplyr::select(
    barcodes,
    cnv_proportion_classification = cnv_mean_classification,
    cnv_sum_classification = cnv_classification
  )

>>>>

```{r}
# get a dataframe with barcodes, sum_classification and cluster_classification 
celltypes_df <- cnv_df |> 
  dplyr::select(
    barcodes,
    cnv_proportion_classification = cnv_mean_classification,
    cnv_sum_classification = cnv_classification,
    mean_cnv_proportion = mean_proportion
  )
